Lott and Mustard Replication

### 2022-04-26 tables/rep_table_2b.tex
fix bacon decomp
final push

\caption{\label{tab:tab:replicatetable2b}Replication of Table 2 (Panel B)}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Variable & N & Mean & Standard Deviation\\
\midrule
\cellcolor{gray!6}{White Male 1019} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0672} & \cellcolor{gray!6}{0.0151}\\
Black Male 1019 & 816 & 0.0102 & 0.0112\\
\cellcolor{gray!6}{Other Male 1019} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0036} & \cellcolor{gray!6}{0.0076}\\
White Female 1019 & 816 & 0.0641 & 0.0149\\
\cellcolor{gray!6}{Black Female 1019} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0101} & \cellcolor{gray!6}{0.0114}\\
\addlinespace
Other Female 1019 & 816 & 0.0035 & 0.0073\\
\cellcolor{gray!6}{White Male 2029} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0741} & \cellcolor{gray!6}{0.0120}\\
Black Male 2029 & 816 & 0.0096 & 0.0104\\
\cellcolor{gray!6}{Other Male 2029} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0035} & \cellcolor{gray!6}{0.0072}\\
White Female 2029 & 816 & 0.0726 & 0.0123\\
\addlinespace
\cellcolor{gray!6}{Black Female 2029} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0104} & \cellcolor{gray!6}{0.0123}\\
Other Female 2029 & 816 & 0.0036 & 0.0073\\
\cellcolor{gray!6}{White Male 3039} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0663} & \cellcolor{gray!6}{0.0118}\\
Black Male 3039 & 816 & 0.0071 & 0.0082\\
\cellcolor{gray!6}{Other Male 3039} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0030} & \cellcolor{gray!6}{0.0066}\\
\addlinespace
White Female 3039 & 816 & 0.0658 & 0.0117\\
\cellcolor{gray!6}{Black Female 3039} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0081} & \cellcolor{gray!6}{0.0098}\\
Other Female 3039 & 816 & 0.0033 & 0.0070\\
\cellcolor{gray!6}{White Male 4049} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0480} & \cellcolor{gray!6}{0.0091}\\
Black Male 4049 & 816 & 0.0046 & 0.0056\\
\addlinespace
\cellcolor{gray!6}{Other Male 4049} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0020} & \cellcolor{gray!6}{0.0047}\\
White Female 4049 & 816 & 0.0483 & 0.0090\\
\cellcolor{gray!6}{Black Female 4049} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0055} & \cellcolor{gray!6}{0.0068}\\
Other Female 4049 & 816 & 0.0022 & 0.0051\\
\cellcolor{gray!6}{White Male 5064} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0580} & \cellcolor{gray!6}{0.0105}\\
\addlinespace
Black Male 5064 & 816 & 0.0052 & 0.0069\\
\cellcolor{gray!6}{Other Male 5064} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0019} & \cellcolor{gray!6}{0.0061}\\
White Female 5064 & 816 & 0.0625 & 0.0123\\
\cellcolor{gray!6}{Black Female 5064} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0065} & \cellcolor{gray!6}{0.0089}\\
Other Female 5064 & 816 & 0.0023 & 0.0069\\
\addlinespace
\cellcolor{gray!6}{White Male 65o} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0426} & \cellcolor{gray!6}{0.0114}\\
Black Male 65o & 816 & 0.0035 & 0.0048\\
\cellcolor{gray!6}{Other Male 65o} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0012} & \cellcolor{gray!6}{0.0046}\\
White Female 65o & 816 & 0.0623 & 0.0167\\
\cellcolor{gray!6}{Black Female 65o} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.0054} & \cellcolor{gray!6}{0.0078}\\
\addlinespace
Other Female 65o & 816 & 0.0014 & 0.0048\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:replicatetable2b}Demographic Variables Summary}
\centering
\begin{tabular}[t]{lrrr}
\toprule
Variable & N & Mean & Standard Deviation\\
\midrule
\cellcolor{gray!6}{White Male 1019} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.067} & \cellcolor{gray!6}{0.015}\\
Black Male 1019 & 816 & 0.010 & 0.011\\
\cellcolor{gray!6}{Other Male 1019} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.004} & \cellcolor{gray!6}{0.008}\\
White Female 1019 & 816 & 0.064 & 0.015\\
\cellcolor{gray!6}{Black Female 1019} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.010} & \cellcolor{gray!6}{0.011}\\
\addlinespace
Other Female 1019 & 816 & 0.004 & 0.007\\
\cellcolor{gray!6}{White Male 2029} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.074} & \cellcolor{gray!6}{0.012}\\
Black Male 2029 & 816 & 0.010 & 0.010\\
\cellcolor{gray!6}{Other Male 2029} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.004} & \cellcolor{gray!6}{0.007}\\
White Female 2029 & 816 & 0.073 & 0.012\\
\addlinespace
\cellcolor{gray!6}{Black Female 2029} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.010} & \cellcolor{gray!6}{0.012}\\
Other Female 2029 & 816 & 0.004 & 0.007\\
\cellcolor{gray!6}{White Male 3039} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.066} & \cellcolor{gray!6}{0.012}\\
Black Male 3039 & 816 & 0.007 & 0.008\\
\cellcolor{gray!6}{Other Male 3039} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.003} & \cellcolor{gray!6}{0.007}\\
\addlinespace
White Female 3039 & 816 & 0.066 & 0.012\\
\cellcolor{gray!6}{Black Female 3039} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.008} & \cellcolor{gray!6}{0.010}\\
Other Female 3039 & 816 & 0.003 & 0.007\\
\cellcolor{gray!6}{White Male 4049} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.048} & \cellcolor{gray!6}{0.009}\\
Black Male 4049 & 816 & 0.005 & 0.006\\
\addlinespace
\cellcolor{gray!6}{Other Male 4049} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.002} & \cellcolor{gray!6}{0.005}\\
White Female 4049 & 816 & 0.048 & 0.009\\
\cellcolor{gray!6}{Black Female 4049} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.005} & \cellcolor{gray!6}{0.007}\\
Other Female 4049 & 816 & 0.002 & 0.005\\
\cellcolor{gray!6}{White Male 5064} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.058} & \cellcolor{gray!6}{0.010}\\
\addlinespace
Black Male 5064 & 816 & 0.005 & 0.007\\
\cellcolor{gray!6}{Other Male 5064} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.002} & \cellcolor{gray!6}{0.006}\\
White Female 5064 & 816 & 0.062 & 0.012\\
\cellcolor{gray!6}{Black Female 5064} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.006} & \cellcolor{gray!6}{0.009}\\
Other Female 5064 & 816 & 0.002 & 0.007\\
\addlinespace
\cellcolor{gray!6}{White Male 65o} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.043} & \cellcolor{gray!6}{0.011}\\
Black Male 65o & 816 & 0.004 & 0.005\\
\cellcolor{gray!6}{Other Male 65o} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.001} & \cellcolor{gray!6}{0.005}\\
White Female 65o & 816 & 0.062 & 0.017\\
\cellcolor{gray!6}{Black Female 65o} & \cellcolor{gray!6}{816} & \cellcolor{gray!6}{0.005} & \cellcolor{gray!6}{0.008}\\
\addlinespace
Other Female 65o & 816 & 0.001 & 0.005\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 tables/twfe.tex
final push

\caption{\label{tab:tab:twfe}Two Way Fixed Effects Shall Issue Coefficients}
\centering
\begin{tabular}[t]{lrr}
\toprule
Outcome Variable & Coefficient & Std. Error\\
\midrule
\cellcolor{gray!6}{Violent Crime Rate Log} & \cellcolor{gray!6}{-0.0977525} & \cellcolor{gray!6}{0.0207145}\\
Property Crime Rate Log & -0.0072047 & 0.0136816\\
\cellcolor{gray!6}{Murder Crime Rate Log} & \cellcolor{gray!6}{-0.0506590} & \cellcolor{gray!6}{0.0385770}\\
Rape Crime Rate Log & -0.0339755 & 0.0271763\\
\cellcolor{gray!6}{Assault Crime Rate Log} & \cellcolor{gray!6}{-0.1004015} & \cellcolor{gray!6}{0.0270163}\\
\addlinespace
Robbery Crime Rate Log & -0.0532480 & 0.0311260\\
\cellcolor{gray!6}{Burglary Crime Rate Log} & \cellcolor{gray!6}{-0.0460697} & \cellcolor{gray!6}{0.0190139}\\
Larceny Crime Rate Log & 0.0033107 & 0.0138442\\
\cellcolor{gray!6}{Autotheft Crime Rate Log} & \cellcolor{gray!6}{-0.0089805} & \cellcolor{gray!6}{0.0282748}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:tab:twfe}Two Way Fixed Effects Shall Issue Coefficients}
\centering
\begin{tabular}[t]{lrr}
\toprule
Outcome Variable & Coefficient & Std. Error\\
\midrule
\cellcolor{gray!6}{Violent Crime Rate Log} & \cellcolor{gray!6}{-0.098} & \cellcolor{gray!6}{0.021}\\
Property Crime Rate Log & -0.007 & 0.014\\
\cellcolor{gray!6}{Murder Crime Rate Log} & \cellcolor{gray!6}{-0.051} & \cellcolor{gray!6}{0.039}\\
Rape Crime Rate Log & -0.034 & 0.027\\
\cellcolor{gray!6}{Assault Crime Rate Log} & \cellcolor{gray!6}{-0.100} & \cellcolor{gray!6}{0.027}\\
\addlinespace
Robbery Crime Rate Log & -0.053 & 0.031\\
\cellcolor{gray!6}{Burglary Crime Rate Log} & \cellcolor{gray!6}{-0.046} & \cellcolor{gray!6}{0.019}\\
Larceny Crime Rate Log & 0.003 & 0.014\\
\cellcolor{gray!6}{Autotheft Crime Rate Log} & \cellcolor{gray!6}{-0.009} & \cellcolor{gray!6}{0.028}\\
\bottomrule
\end{tabular}
\end{table}

### 2022-04-26 writing/paper.tex
final push

As shown by the figure, it is not clear the pretrend assumptions hold. Indeed, for many years prior to the treatment year, the estimated effect is statistically significantly different from zero with a 95 percent confidence interval. Additionally, we notice that we see no average treatment effect for the first few years after treatment, before a significant departure for a few years followed by a reversion.

>>>>

As shown by the figure, it is not clear the pretrend assumptions hold. Indeed, for many years prior to the treatment year, the estimated effect is statistically significantly different from zero with a 95 percent confidence interval. Additionally, we notice that we see no average treatment effect for the first few years after treatment, before a significant departure for a few years followed by a reversion. The arc is slightly worrisome from a result perspective, since we have significant imbalance for more than three years of treatment in our sample and this is where the most significant results appear. Of the eighteen states with shall issue laws in the sample, ten have more than three years of treatment while eight do not. Thus, the results out past this point are not as strong as those immediately following treatment.
